---
title: "Data Analysis for BRP with Corridor Method"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(dplyr)
```

This file allows to summarize the results of the CM algorithm for BRP. The 
algorithm is the one presented in the OR Spectrum paper (2008), with a fix carried
out in April 2017. I realized that the maximum height limit was not respected by
the corridor selection mechanism. Therefore, I was obtaining solutions for which
the maximum height (typically, H+2) was violated. That "bug" has been fixeed in 
the current version of the code (which is also the one on github). Upon request
from SV, I re-run all the instances of the paper and collected the average values
per class. In addition, the raw data (i.e., instance-by-instance result) has also
been collected. If we want to get the evolution of the bay for each instance,
a flag (#define W_PATH) should be activated in the code. This will allow to print 
on screen the path followed to reach the best solution found.

```{r}
inp = read.table("results17All.dat")
#inp = read.table("result17-All.dat")
#inp = read.table("result17-Large.dat")
# this is to filter out non-solutions
inp = inp %>% 
  filter(V7 != -999)
str(inp)
inp = rename(inp, moves = V5)
inp = rename(inp, corridor = V6)
inp = rename(inp, time = V7)
```
Add columns with H (height), W (width), and Instance Number. NOTE: use 4,3,2
for small instances, while 3,2,1 for larger instances. This is due to the different
format of the filename:
```{r}
n = dim(inp)[1]
a = vector()
for (i in seq(1:n)) {a[i] = as.numeric(unlist(regmatches(inp$V1[i],gregexpr("[[:digit:]]+",inp$V1[i]))))[3]}
inp = inp %>%
  mutate(InstNr = a)
for (i in seq(1:n)) {a[i] = as.numeric(unlist(regmatches(inp$V1[i],gregexpr("[[:digit:]]+",inp$V1[i]))))[2]}
inp = inp %>%
  mutate(W = a)
for (i in seq(1:n)) {a[i] = as.numeric(unlist(regmatches(inp$V1[i],gregexpr("[[:digit:]]+",inp$V1[i]))))[1]}
inp = inp %>%
  mutate(H = a)
```

Analysis per instance class. Creation of raw data files for each instance class:
```{r}
Ht = 5
#Wt = 10
for (Wt in c(4))
#for (Ht in c(6,10)){
#for (Wt in c(6,10))
{
  
summaryClass = inp %>%
  filter(H==Ht, W==Wt) %>%
  group_by(InstNr) %>%
  summarise(n(), min(moves), max(moves))
filename = paste(c("raw-",Ht,"-",Wt,".csv"),collapse = "")
write.csv(summaryClass,filename)
} 
#}
```

Finally, global analysis. We get the average number of relations for each instance
class. Note: CHANGE name files, to avoid overwriting results for different classes:
```{r}
summaryAll = inp %>%
  group_by(H,W,InstNr) %>%
  summarise(moves = min(moves))
write.csv(summaryAll,"rawAll.csv")


avgTable = summaryAll %>%
  group_by(H,W) %>%
  summarise(n(), mean(moves))
write.table(avgTable, "avgTable.txt", sep="\t")
```


